Scalar on Function Regression

### 2022-01-07 Presentation/slides.tex
To add images

	\begin{frame}{Plots}
		Two plots of stock and human growth
	\end{frame}

@@

	\begin{frame}{Plots of Basis Functions }
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 3.5cm]{../Graphics/Bspline_Basis.pdf}
			\includegraphics[height = 3.5cm]{../Graphics/Fourier_Basis.pdf}
		\end{minipage}
	\end{frame}

@@

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 7cm]{../Graphics/Trade_off.png}
		\end{minipage}
	\end{frame}

>>>>

	\begin{frame}{Plots}
		\begin{figure}
			\centering
			\begin{minipage}{.5\textwidth}
				\centering
				\includegraphics[width=\textwidth]{../Graphics/Growth_curves.png}
				\caption{\tiny Growth curves of 54 girls age 1-18}
			\end{minipage}%
			\begin{minipage}{.5\textwidth}
				\centering
				\includegraphics[width=\textwidth]{../Graphics/NIR.png}
				\caption {\tiny NIR spectrum of 60 gasoline samples}
			\end{minipage}
		\end{figure}
	\end{frame}

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
			\caption {Fourier basis functions with order 9}
		\end{figure}

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline Basis with order 9}
		\end{figure}
	\end{frame}

@@

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 7cm]{../Graphics/Tradeoff.png}
		\end{minipage}
	\end{frame}
